---
name: Reka Solymosi
position: "Senior Lecturer in Quantitative Methods"
address: "School of Social Sciences, University of Manchester"
phone: +44 161 275 3468
www: rekadata.net
email: reka.solymosi@manchester.ac.uk
twitter: r_solymosi
github: maczokni
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library("lubridate")
library("rorcid")
library("vitae")
library("tidyverse")

my_orcid <- "0000-0001-8689-1526"

#Matt's workaround because biber cannot handle filepaths with space in them, and UoM dropbox doesn't let me change its name
#copy citation files into temporary locations where biber can read from:
citations_0 <- tempfile(fileext = ".bib")
file.copy(from = here::here("public/cv/books.bib"), to = citations_0)
citations_1 <- tempfile(fileext = ".bib")
file.copy(from = here::here("public/cv/published.bib"), to = citations_1)
citations_2 <- tempfile(fileext = ".bib")
file.copy(from = here::here("public/cv/accepted.bib"), to = citations_2)
citations_3 <- tempfile(fileext = ".bib")
file.copy(from = here::here("public/cv/underreview.bib"), to = citations_3)
citations_4 <- tempfile(fileext = ".bib")
file.copy(from = here::here("public/cv/otherpubs.bib"), to = citations_4)
```


# Education and Qualifications

```{r education}

orcid_educations(my_orcid) %>% 
	pluck(my_orcid, "affiliation-group", "summaries") %>% 
	{ do.call("rbind", .) } %>% 
	brief_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`}-{`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`
	)
```


# Present and previous appointments

```{r employment}
orcid_employments(my_orcid) %>% 
	pluck(my_orcid, "affiliation-group", "summaries") %>% 
	{ do.call("bind_rows", .) } %>%
	brief_entries(
		what = `employment-summary.role-title`,
		when = paste0(
			format(ymd(paste(`employment-summary.start-date.year.value`,
											 `employment-summary.start-date.month.value`,
											 `employment-summary.start-date.day.value`)), "%b %Y"), 
			"-",
			ifelse(is.na(`employment-summary.end-date.year.value`),
						 "present",
						 format(ymd(paste(`employment-summary.end-date.year.value`,
											 `employment-summary.end-date.month.value`,
											 `employment-summary.end-date.day.value`)), "%b %Y"))
		),
		with = glue::glue("{`employment-summary.department-name`}, {`employment-summary.organization.name`}")
	)
```

<!-- # Professional qualifications -->

<!-- ```{r qualifications} -->
<!-- orcid_qualifications(my_orcid) %>%  -->
<!-- 	pluck(my_orcid, "affiliation-group", "summaries") %>%  -->
<!-- 	{ do.call("rbind", .) } %>%  -->
<!-- 	brief_entries( -->
<!-- 		what = `qualification-summary.role-title`, -->
<!-- 		when = `qualification-summary.start-date.year.value`, -->
<!-- 		with = `qualification-summary.organization.name` -->
<!-- 	) -->
<!-- ``` -->

# Publications


My research areas include perception of crime and place, spatial crime analysis, environmental criminology, social data science, transport crime, crowdsourcing, and geographical information analysis.


ORCID: `r my_orcid`

## Books


```{r books}
bibliography_entries(citations_0) 
```

## Peer reviewed publications


```{r publications}
bibliography_entries(citations_1) 
```

# Research Grants

```{r fundingpi}
tribble(
	~title, ~start_date, ~end_date, ~value, ~funder,
	"Exploring perceptions of direct and indirect bystander intervention", 2022, 2022, "GBP 8,930", "School of Social Sciences Research Support Funds 2021-22",
	"Geoprivacy, confidentiality and data sharing in research & practice", 2022, 2022, "GBP 4,293", "KTH Royal Institute of Technology and Stockholm University Joint Research Seed Fund",
	"Understanding changing demand for police during the coronavirus pandemic", 2020, 2021, "GBP 20,000", "N8 Policing Research Partnership",	
	"Civic InnovatioN in CommunITY: safety, policing and trust with young people", 2019, 2020, "GBP 60,000", "EPSRC Network+: Social Justice through the Digital Economy",
	"Identifying features that affect public engagement with appeals for information about missing persons on Twitter", 2019, 2019, "GBP 5,000", "Manchester Statistical Society Campion Grant",
	"Measuring fear of crime using app-based and sensing methodologies", 2017, 2020, "GBP 10,000", "British Academy and Leverhulme Small Grants",
	"Using Bayesian Surprise maps to explore debt and insolvency across the UK", 2018, 2019, "GBP 10,000", "Consumer Data Research Centre, Economic and Social Research Council",
	"Building Tools and Training for Crime Analysts using R", 2017, 2017, "GBP 3,000", "N8 Policing Research Partnership", 
	"Data Visualisation in Criminal Courts", 2017, 2017, "GBP 1,000", "Economic Social Research Council, Festival of Social Sciences"
) %>% 
	arrange(desc(start_date)) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		when = glue::glue("{`start_date`}-{`end_date`}"),
		with = glue::glue("{`value`} funding from {`funder`}")
	)
```

# Invited talks

```{r invitedtalks}
tribble(
	~title, ~date, ~venue, 
	"Hot Routes and Street Profiles", "2022", "Netherlands Institute for the Study of Crime and Law Enforcement",
	
	"Near Misses in Research on Crime and Fear of Crime", "", "Crest Advisory Internal Seminar",
	
	"Even beautiful maps can be misleading", "", "Ministry of Defence, Defence Science and Technology Lecture Series",
	
	"New forms of data for public safety", "2021", "Mexico National Institute of Statistics and Geography (INEGI)",
	
	"Understanding people's experiences and perceptions of place, crime, and victimisation using crowdsourced data", "2020", "Monash University, Melbourne, Australia", 
	
		"Exploring the role of crowdsourced data in criminal justice research", "", "Queensland University of Technology, Melbourne, Australia", 
	
	"Mapping and spatial modelling in R for crime prevention and conservation", "2019","Sheffield R User Group, UK",
	
	"The role of innovative data collection methods in advancing understanding, and the importance of considering the biases within", "","Women in Data Science: Zurich, Switzerland",
	
	"Keynote: Data-driven insights in law: opportunities and cautions", "","Berlin Legal Tech Conference 2019, Germany",
	
	"The role of innovative data collection methods in advancing behavioural understanding", "", "Cognitive and Decision Sciences, University of Basel, Switzerland",
	
	"The role of innovative data collection methods in advancing criminological understanding","","Manchester Metropolitan University Big Data Centre Seminar Series, UK",
	
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		when = glue::glue("{`date`}"),
		with = glue::glue("{`venue`}")
	)
```

