---
name: Reka Solymosi
position: "Lecturer in Quantitative Methods"
address: "School of Social Sciences, University of Manchester"
phone: +44 161 275 3468
www: rekadata.site
email: reka.solymosi@manchester.ac.uk
twitter: r_solymosi
github: maczokni
# linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library("lubridate")
library("rorcid")
library("vitae")
library("tidyverse")

my_orcid <- "0000-0001-8689-1526"
```


# Employment

```{r employment}
orcid_employments(my_orcid) %>% 
	pluck(my_orcid, "affiliation-group", "summaries") %>% 
	{ do.call("bind_rows", .) } %>%
	brief_entries(
		what = `employment-summary.role-title`,
		when = paste0(
			format(ymd(paste(`employment-summary.start-date.year.value`,
											 `employment-summary.start-date.month.value`,
											 `employment-summary.start-date.day.value`)), "%b %Y"), 
			"–",
			ifelse(is.na(`employment-summary.end-date.year.value`),
						 "present",
						 format(ymd(paste(`employment-summary.end-date.year.value`,
											 `employment-summary.end-date.month.value`,
											 `employment-summary.end-date.day.value`)), "%b %Y"))
		),
		with = glue::glue("{`employment-summary.department-name`}, {`employment-summary.organization.name`}")
	)
```


# Education

```{r education}
orcid_educations(my_orcid) %>% 
	pluck(my_orcid, "affiliation-group", "summaries") %>% 
	{ do.call("rbind", .) } %>% 
	brief_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`}–{`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`
	)
```


<!-- # Professional qualifications -->

<!-- ```{r qualifications} -->
<!-- orcid_qualifications(my_orcid) %>%  -->
<!-- 	pluck(my_orcid, "affiliation-group", "summaries") %>%  -->
<!-- 	{ do.call("rbind", .) } %>%  -->
<!-- 	brief_entries( -->
<!-- 		what = `qualification-summary.role-title`, -->
<!-- 		when = `qualification-summary.start-date.year.value`, -->
<!-- 		with = `qualification-summary.organization.name` -->
<!-- 	) -->
<!-- ``` -->


# Publications

ORCID: `r my_orcid`


Peer reviewed publications


```{r publications}
bibliography_entries("published.bib", "", 
										 sorting = "ydnt") %>% 
	mutate(journal = ifelse(is.na(journal) & bibtype == "Article",
													paste("pre-print on", publisher),
													journal))
```



Forthcoming: publications under review for which pre-prints are available. OSF profile: [osf.io/3nzk2](osf.io/3nzk2).

```{r forthcoming}
bibliography_entries("forthcoming.bib", "", 
										 sorting = "ydnt") %>% 
	mutate(journal = ifelse(is.na(journal) & bibtype == "Article",
													paste("pre-print on", publisher),
													journal))
```


Other outputs

```{r otherpubs}
bibliography_entries("otherpubs.bib", "", 
										 sorting = "ydnt")
```

# Funding

Funding awarded as Principal Investigator


```{r fundingpi}
tribble(
	~title, ~start_date, ~end_date, ~value, ~funder,
	"Identifying features that affect public engagement with appeals for information about missing persons on Twitter", 2019, 2019, "£5,000", "Manchester Statistical Society Campion Grant",
	"Measuring fear of crime using app-based and sensing methodologies", 2017, 2020, "£10,000", "British Academy and Leverhulme Small Grants",
	"Using Bayesian Surprise maps to explore debt and insolvency across the UK", 2018, 2019, "£10,000", "Consumer Data Research Centre, Economic and Social Research Council",
	"Building Tools and Training for Crime Analysts using R", 2017, 2017, "£3,000", "N8 Policing Research Partnership", 
	"Data Visualisation in Criminal Courts", 2017, 2017, "£1,000", "Economic Social Research Council, Festival of Social Sciences"
) %>% 
	arrange(desc(start_date)) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		when = glue::glue("{`start_date`}–{`end_date`}"),
		with = glue::glue("{`value`} funding from {`funder`}")
	)
```


Funding awarded as Co Investigator


```{r fundingci}
tribble(
	~title, ~start_date, ~end_date, ~value, ~funder,
	"Civic InnovatioN in CommunITY: safety, policing and trust with young people", 2019, 2020, "£30,000", "EPSRC Network+: Social Justice through the Digital Economy"
) %>% 
	arrange(desc(start_date)) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		when = glue::glue("{`start_date`}–{`end_date`}"),
		with = glue::glue("{`value`} funding from {`funder`}")
	)
```




# Teaching

University of Manchester Graduate Level Courses


```{r teachingpgt}
tribble(
	~title, ~start_date, ~end_date, ~code, ~level,
	"Designing Criminological Research", 2016, "present", "LAWS70311", "Course director and primary lecturer on compulsory research methods module for all Masters streams",
	"Data Analysis with R & R Studio", 2016, 2019, "LAWS70821", "2016: Course director and sole lecturer, 2018 onwards: ad-hoc lecturer on introductory statistics for MRes students using R",
	"Evaluating Policy and Practice", 2018, 2019, "LAWS70542", "Lecturer on mandatory module for all Masters streams introducing evaluation research beyond academia"
) %>% 
	arrange(desc(start_date)) %>% 
	brief_entries(
		what = glue::glue("{`code`}: {`title`}"),
		when = glue::glue("{`start_date`}–{`end_date`}"),
		with = glue::glue("{`level`}")
	)
```


University of Manchester Undergraduate Level Courses


```{r teachingug}
tribble(
	~title, ~start_date, ~end_date, ~code, ~level,
	"Making Sense of Criminological Data", 2016, "present", "LAWS20441", "Introduction to quantitative research for 2nd year undergraduates.",
	"Modelling Criminological Data", 2017, "present", "LAWS20452 ", "Inferential statistics course for 2nd year undergraduates.",
	"Crime Mapping: An introduction to GIS and spatial analysis", 2018, "present", "LAWS31152", "Basics of spatial data visualisation and analysis for 3rd year undergraduate and all graduate students.",
	"Short Dissertation", 2017, "present", "LAWS30620", "Lectures and supervision of students on secondary data analysis pathway for their final year dissertation."
	
) %>% 
	arrange(desc(start_date)) %>% 
	brief_entries(
		what = glue::glue("{`code`}: {`title`}"),
		when = glue::glue("{`start_date`}–{`end_date`}"),
		with = glue::glue("{`level`}")
	)
```


Other teaching, short courses, and guest lecturing


```{r teachingother}
tribble(
	~title, ~start_date, ~end_date, ~code, ~level,
	"Getting Started in R: introduction to data analysis & visualisation", 2017, "present", "methods@manchester", "Weeklong intensive course introducing students to using R and R Studio for data analysis. Open to all, usually attended by professionals and academics.",
	"Introduction to mapping data with QGIS", 2017, "present", "Q-Step internship preparation", "Afternoon short introduction to mapping spatial data for Q-step internship students",
	"Spatial Data Analysis in Practice", 2017, 2017, "Stockholm Royal Institute of Technology (KTH)", "One-day introduction to mapping with QGIS and data collection from APIs as part of weeklong summer school for PhD students",
	"Trasport Safety and Security", 2012, 2017, "University College London MSc Transport Studies", "Guest lecture for graduate module, UCL Department of Civil, Environmental, and Geomatic Engineering",
	"Data analysis using R", 2019, 2019, "Research IT", "One-day introduction to R, part of University of Manchester's Research IT series of courses for staff and PhD students."
	
) %>% 
	arrange(desc(start_date)) %>% 
	brief_entries(
		what = glue::glue("{`code`}: {`title`}"),
		when = glue::glue("{`start_date`}–{`end_date`}"),
		with = glue::glue("{`level`}")
	)
```


# Invited talks

2019
```{r invitedtalks2019}
tribble(
	~title,  ~venue, 
	"Mapping and spatial modelling in R for crime prevention and conservation","Sheffield R User Group, UK",
	"The role of innovative data collection methods in advancing understanding, and the importance of considering the biases within","Women in Data Science: Zurich, Switzerland",
	"Keynote: Data-driven insights in law: opportunities and cautions", "Berlin Legal Tech Conference 2019, Germany",
	"The role of innovative data collection methods in advancing behavioural understanding", "Cognitive and Decision Sciences, University of Basel, Switzerland",
	"The role of innovative data collection methods in advancing criminological understanding","Manchester Metropolitan University Big Data Centre Seminar Series, UK"
	
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2018
```{r invitedtalks2018}
tribble(
	~title,  ~venue, 
	"Interdisciplinary Alchemy: Data Science + Social Science","Data Kind UK",
	"Everybody Lies but Not Everybody Tweets: Making Sense of the Bias in Your Data","Advances in Data Science conference, Manchester, UK"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2017
```{r invitedtalks2017}
tribble(
	~title,  ~venue, 
	"Reproducible Crime Analysis using R","Intelligence Innovation Working Group hosted by West Midlands Police",
	"Building Interactive Data Visualizations","Manchester Methods Fair, UK",
	"Using open data in the social sciences", "Her+Data Meetup, Manchester, UK",
	"What is Crowdsourced Data?","Methods@Manchester seminar on research methods in social sciences, Manchester,UK", 
	"Eyes and Apps on the Street", "Stockholm Royal Institute of Technology (KTH), Sweden",
	"Keynote: Making Sense of Data using Methods","Methods North West Launch Conference, Manchester, UK", 
	"Using R for Crime Analysis", "Greater Manchester Police, Force HQ, Manchester, UK",
	"Mapping	fear	of	crime	as	a	context-dependent	everyday	experience	that	varies	in	space	and	time","Horizon 2020 Project MARGIN conference, Budapest, Hungary",
	"Using open data to evaluate current approaches to cabs tasking", "11th International Crime Science Conference, London, UK",
	"Fighting Crime (and other bad things) on the transport network", "Manchester R User Group meetup"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2016
```{r invitedtalks2016}
tribble(
	~title,  ~venue, 
	"Practitioner-Academic Seminar on Confidence in Policing","Transport for London, UK",
	"Policing and Public Confidence - Confidence at TfL and the challenges of a transport environment","Public Confidence in the Police - University of Warwick, UK"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2015
```{r invitedtalks2015}
tribble(
	~title,  ~venue, 
	"Scheduling student-led learning by enquiry into the curriculum","Teaching and Learning Conference 2015, UCL, London, UK",
	"Alternative Denominators in Transport Crime Rates","Transport Statistics User Group Meeting, London, UK",
	"Using a smartphone app to measure fear of crime on route 25","Transport for London Route 25 Joint Transport Action Group (JTAG) meeting, London, UK"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2014
```{r invitedtalks2014}
tribble(
	~title,  ~venue, 
	"Streets, Crime, and Transport","EPSRC Impact Award Seminar, London, UK",
	"A new approach to mapping perceptions of crime along the door-to-door journey","Transport Geography Research Group Workshop, Leeds, UK",
	"Fear of crime on transport","PopFest, annual Population Studies conference for PhD students, London, UK",
	"Using a smartphone app to report fear of hate crime","Trans London Meetup, London, UK"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2013
```{r invitedtalks2013}
tribble(
	~title,  ~venue, 
	"Crowd spatial patterns at bus stops","Stockholm Royal Institute of Technology (KTH), Sweden"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


# Conference presentations

2019
```{r conf2019}
tribble(
	~title,  ~venue, 
	"Linking app-based and physiological measures of fear of crime","Environmental Criminology and Crime Analysis Symposium, Gungzhou China",
		"Mapping Sexual Harassment in Public Places: Open Source Data Driven Contextual Analysis","Environmental Criminology and Crime Analysis Symposium, Gungzhou China"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```

2018
```{r conf2018}
tribble(
	~title,  ~venue, 
	"Victimization and perceived safety among college students: Focus on women's transit safety in London, UK","Crime and fear in public places: KTH Royal Institute of Technology, Stockholm, Sweden",
		"Measuring fear of crime through app-based and sensing methodologies","Crime and fear in public places: KTH Royal Institute of Technology, Stockholm, Sweden"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```

2017
```{r conf2017}
tribble(
	~title,  ~venue, 
	"Using open data to evaluate current approaches to cabs tasking","American Society of Criminology Conference, Philadelphia, USA",
	"Using open data to evaluate current approaches to cabs tasking","Environmental Criminology and Crime Analysis Symposium, El Salvador",
	"Active Participant","R Open Science Unconference, Los Angeles, USA"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```



2015
```{r conf2015}
tribble(
	~title,  ~venue, 
	"Using open crowdsourced data to map signal crimes in place and time","Environmental Criminology and Crime Analysis Symposium, New Zealand",
	"Alternative Denominators in Transport Crime Rate","Stockholm Symposium for Criminology, Sweden"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2014
```{r conf2014}
tribble(
	~title,  ~venue, 
	"Mapping Fear of Crime Dynamically in Place and Time: Case study of Revenue Protection Inspectors on a London Bus Route","American Society of Criminology, San Francisco, USA"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


2013
```{r conf2013}
tribble(
	~title,  ~venue, 
	"Participatory mapping of fear of crime using a mobile phone application","Urban Data Management Symposium, London, UK"
) %>% 
	brief_entries(
		what = glue::glue("{`title`}"),
		with = glue::glue("{`venue`}")
	)
```


# Memberships

- **Curriculum Advisory Board Member** Data Carpentry Social Sciences Curriculum
- **Fellow** Software Sustainability Institute
- **Associate Fellow** Higher Education Academy
- **Board Member** ESRC Business and Local Government Data Research Centre Data Acquisition Board
- **Member** Environmental Criminology and Crime Analysis Symposium 
- **Member** Transport Crime Research Network


