---
name: Dr Reka Solymosi
position: "Lecturer in Quantitative Methods"
address: "School of Social Sciences, University of Manchester"
phone: +44 792 333 6615
www: rekadata.site
email: reka.solymosi@manchester.ac.uk
twitter: r_solymosi
github: maczokni
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library("lubridate")
library("rorcid")
library("vitae")
library("tidyverse")

my_orcid <- "0000-0001-8689-1526"
```



# Present and previous appointments

```{r employment }

lineb <- '\\\\'
tribble(
	~title, ~subtitle, ~start_date, ~end_date, ~value, ~p1, ~p2,
	"Lecturer (Asst Prof)"," in Quantitative Methods", 2016, "present",
	"University of Manchester, Department of Social Sciences",
	"Carry out research, secure grant funding, manage research teams, and engage with industry and public sector to maximise impact.",
	"Teaching (eg: quantitative data analysis, GIS and crime mapping, evaluation research).",


	"Data Analyst","", 2015, 2016,
	"Transport for London, Enforcement and On Street Operations Directorate",
	"Gather, process, and analyse data on trends and emerging issues by preparing analytical products, which informed TfL's deployment decisions.",
	"Collated data from diverse sources to make them useful by cleaning and writing code for reproducible data pipelines from query to output report or interactive applications.",


	"Data Analyst","", 2014, 2014,
	"London Borough of Camden, Transport and Street Planning Team",
	"Apply a mixed methods approach to analyse and report on data collected from public consultation, to allow for tailored responses from the council to a diverse range of stakeholders.",
	"",


		"Research Assistant","", 2011, 2014,
	"University College London, Community-based Open Mapping to Engage Travel project (PT)",
	"Develop, pilot test (including reliability and validity testing), and deploy a longitudinal diary-style questionnaire aimed to allow wheelchair users to report the perveived difficulty of specific journeys",
	"Synchronise GPS, accelerometer data and smart sensor data with self-report measures.",


	"Teaching Assistant","", 2010, 2015,
	"University College London",
	"Department of Geography, Department of Civil Environmental and Geographic Engineering",
	"(PT)",

	"Research Administrator","", 2011, 2014,
	"University College London",
	"Pedestrian Accessibility and Movement Environment Laboratory",
	"(PT)"
) %>%
	arrange(desc(start_date)) %>%
 detailed_entries(
		what = glue::glue("{`value`}: {`start_date`}-{`end_date`}"),
		when = ifelse(nchar(subtitle) <1,`title`, paste(glue::glue("{`title`}"), glue::glue("{`subtitle`}"), sep = "\\\\")),
		where = ifelse(nchar(p2) <1,`p1`, glue::glue("{`p1`} {`p2`}")),
		.protect = FALSE
	)

```

# Education and Qualifications

```{r education}

orcid_educations(my_orcid) %>% 
	pluck(my_orcid, "affiliation-group", "summaries") %>% 
	{ do.call("rbind", .) } %>% 
	brief_entries(
    when = `education-summary.role-title`,
    with = glue::glue("{`education-summary.start-date.year.value`}-{`education-summary.end-date.year.value`}"),
    what = `education-summary.organization.name`
	)
```



# Selected Research Activities 

 $\bullet$ **Peer reviewed academic publications** in high-ranking journals on topics around methodological innovation in social science research (see [Google Scholar](https://scholar.google.com/citations?user=IXexMmEAAAAJ&hl=en) and [ORCID](https://orcid.org/0000-0001-8689-1526))


 $\bullet$ **Research reports and blog posts** on prestigious research forums such as [LSE Impact Blog](https://blogs.lse.ac.uk/impactofsocialsciences/2019/08/14/using-mobile-applications-for-social-science-research/) and [Social Research Association Blog](https://the-sra.org.uk/SRA/Blog/Harry%20Potter,%20Pet%20Names%20and%20Bag%20theft%20Communicating%20Crime%20Data%20and%20Analysis%20to%20Young%20People.aspx)


 $\bullet$ **Conference presentations** at academic and industry venues (eg: [Women in Data Science](https://www.linkedin.com/pulse/wids-zurich-sparks-inspires-daniel-martin-eckhart/), [TicTec](https://tictec.mysociety.org/2018/speaker/reka-solymosi))

# Professional memberships 

Fellow of Software Sustainability Institute $\bullet$ Board Member of the Data Carpentries Social Sciences Curriculum $\bullet$ Fellow of the Higher Education Academy $\bullet$ Board Member of Economic and Social Research Council Business and Local Government Data Research Centre's Data Acquisition Board $\bullet$ R-Ladies Member $\bullet$ Honorary Lecturer at University College London


# List of skills

Quantiative and qualitative data analysis  $\bullet$ Spatial data analysis and GIS mapping $\bullet$ Data collection, cleaning, and wrangling $\bullet$ Written and oral communication skills $\bullet$ Version control using git $\bullet$ Data query using SQL, APIs, webscraping $\bullet$ Coding languages: R, Java, SQL, Python  $\bullet$ Software: Microsoft Office Suite, QGIS, ArcGIS, MapInfo
